### 2017-03-01 paper/chapters/gan.tex
added name for name

\subsubsection{(Virtual) Batch normalization}
\label{ssub:gan_batch_norm}
% TODO explain internal covariate shift?
Batch normalization (BN) \cite{batch_norm:2015} is a recent technique to boost performance in deep neural networks addressing the \emph{internal covariate shift} by normalizing minibatches.
Essentially, BN works by normalizing each sample from a minibatch to the statistics of the whole batch.
To improve training performance of GANs, a modified version of batch normalization has been proposed \cite{improved_gan:2016} for training of the generator.
Instead of normalizing each input $x$ to their corresponding minibatch, one reference batch is chosen prior to training which will be used to normalize all further input.

>>>>

\subsubsection{(Virtual) Batch normalization}
\label{ssub:gan_batch_norm}
% TODO explain internal covariate shift?
Batch normalization (BN) \cite{batch_norm:2015} is a recent technique to boost performance in deep neural networks addressing the \emph{internal covariate shift} by normalizing minibatches.
Essentially, BN works by normalizing each sample from a minibatch to the statistics of the whole batch.
To improve training performance of GANs, a modified version of batch normalization called virtual batch normalization has been proposed \cite{improved_gan:2016} for training of the generator.
Instead of normalizing each input $x$ to their corresponding minibatch, one reference batch is chosen prior to training which will be used to normalize all further input.
